### 2018-01-19 manuscript.rmd
edited affilations, names

Catriona Munro^1^\*, Stefan Siebert^1,2^\*, Felipe Zapata^1,3^, Mark Howison^4,6^, Alejandro Damian Serrano^1,10^, Samuel H Church^1,6^, Freya Goetz^1,7^, Phil Pugh^8^, Steven H.D. Haddock^9^, Casey W. Dunn^1,10^**

>>>>

Catriona Munro^1^\*, Stefan Siebert^1,2^\*, Felipe Zapata^1,3^, Mark Howison^4,5^, Alejandro Damian Serrano^1,10^, Samuel H. Church^1,6^, Freya Goetz^1,7^, Philip R. Pugh^8^, Steven H.D. Haddock^9^, Casey W. Dunn^1,10^**
